---
title: "Moringa_school_IP_Week14_Dimension Analysis_Feature_selection"
author: "Mutura Kuria"
date: "2/7/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# 1.0 Business Understanding

Carrefour Kenya and are currently undertaking a project that will inform the marketing department on the most relevant marketing strategies that will result in the highest no. of sales (total price including tax). Your project has been divided into four parts where you'll explore a recent marketing dataset by performing various unsupervised learning techniques and later providing recommendations based on your insights.

2.0 Loading the Dataset

```{r}
data1 <- read.csv("http://bit.ly/CarreFourDataset")
head(data1)
```
```{r}
#Summaryzing the data
summary((data1))
```
# 3.0 Cleaning our Data
 ## 3.1 Check duplicated data
 
```{r}
#Checking for duplicated rows
duplicated_rows <- data1[duplicated(data1),]
dim(duplicated_rows)
```
 
  -We have no duplicates
  
  
## 3.2 Missing Values

```{r}
# Checking for Missing Values

colSums(is.na(data1))
```
  - Wehave no missing values
  
# 3.3 Dropping unneccessary columns

```{r}
# dropping Invoice.ID column
data1$Invoice.ID <- NULL
```
```{r}
head(data1)

```

## 3.4 Converting data to appropriate datatypes

```{r}
# Convert data types to intergerst 

data2 <- data1
data2$Branch_Enc<-as.integer(as.factor(data2$Branch))
# Customer Type
data2$Customer_Type_Enc<-as.integer(as.factor(data2$Customer.type))
# Gender
data2$Gender_Enc<-as.integer(as.factor(data2$Gender))
# Product.line
data2$Product_Line_Enc<-as.integer(as.factor(data2$Product.line))
#Payment
data2$Payment_Enc<-as.integer(as.factor(data2$Payment))
```

```{r}
str(data2)
```

```{r}
# Convert time to appropriate format
data2$hour = format(strptime(data2$Time,"%H:%M"),'%H')
data2$minute = format(strptime(data2$Time,"%H:%M"),'%M')
```

```{r}
install.packages("lubridate") 
library(lubridate)
```


```{r}
# Split date year, month and day. and change data type
data2$Date <- as.Date(data2$Date, "%m/%d/%Y")
data2$year <- year(ymd(data2$Date))
data2$month <- month(ymd(data2$Date)) 
data2$day <- day(ymd(data2$Date))
```
```{r}
str(data2)
```
# 4.0 Dimensionality Reduction

##Selecting Numeric fields
```{r}
library(dplyr)
```


```{r}
num <- select_if(data2,is.numeric)
str(num)
```

## 4.1 Principal Component Analysis (PCA)

```{r}
# Drop the columns a constant/zero column to unit variance")"
num <- subset(num, select = -c(gross.margin.percentage, year))


```

```{r}
dim(num)
```
```{r}
# Performing PCA with center and scale set to true
num.pca <- prcomp(num, center = TRUE, scale. = TRUE)

# summary
summary(num.pca)
```

  --We get 14 principle components. With Pc1 having 22% variance while Pc10 having up to 95%, pca 11 to 14 should be dropped. We can compare this with t-SNE results

## Stochastic Neighbour Embedding(t-SNE)

```{r}
library(Rtsne)
tsne <- Rtsne(num, dims = 2, perplexity=30, verbose=TRUE, max_iter = 500)
```
```{r}
num$Rating_num = as.integer(num$Rating)

# Curating the database for analysis 
# 
Labels<-num$Rating_num
num$Rating_num<-as.factor(num$Rating_num)

# For plotting
colors = rainbow(length(num$Rating_num))
names(colors) = unique(num$Rating_num)

plot(tsne$Y, t='n', main="tsne")
text(tsne$Y, labels=num$Rating_num, col=colors[num$Rating_num])
```


